\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[hidelinks]{hyperref}
    \usepackage[left=2cm, right=2cm, top=2cm]{geometry}
    \usepackage{longtable}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
    \vspace*{-40pt}

    

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace*{-2pt}
  \begin{center}
    {\Huge \scshape {Syed Mohammad Huzaif}}\\
    \vspace*{2pt}
    
    \vspace*{2pt}
    \href{mailto:syedhuzaif199@gmail.com}{syedhuzaif199@gmail.com} | \href{tel:+919149728459}{+91 91497 28459} | \href{tel:+917889426710}{+91 78894 26710}\\
    \vspace*{2pt}
    \textbf{\href{https://github.com/syedhuzaif199}{github.com/syedhuzaif199}}
  \end{center}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Experience
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Experience}
    \vspace{2mm}
        \textbf{Orchardly}\hfill Srinagar, Jammu and Kashmir, IN\\
    Junior Backend Developer\hfill 1 Jan 2025 - Present\\
    \vspace{-2mm}
    \begin{itemize}
    \item[] Developing the backend for a scalable e-commerce platform using Laravel, designing and implementing RESTful APIs to support seamless integration with frontend systems and third-party services.

    \item[] Collaborated with a senior developer to redesign the database schema, optimizing performance, scalability, and data integrity to accommodate complex agricultural product workflows and high transaction volumes.

    \item[] Modernized application architecture by introducing Data Objects and Action Patterns, decoupling business logic from controllers and enhancing code maintainability, testability, and scalability.
    \end{itemize}
      \vspace{2mm}
      \textbf{Yarikul Infotech}\hfill Srinagar, Jammu and Kashmir, IN\\
    Software Development Intern \hfill 20 Nov 2024 - 31 Dec 2024\\
    \vspace{-2mm}
    \begin{itemize}
    \item[] Developed a small E-commerce platform using PHP, Laravel and SQLite
    \end{itemize}

    \vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Education
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Education}
      \vspace{2mm}
      \textbf{University of Kashmir}\hfill Jammu and Kashmir, IN\\
Full-time Bachelor of Technology in Computer Science and Engineering \hfill Nov 2020 - Oct 2024\\
{\sl GPA: 8.41}\\
\vspace{2mm}
      \textbf{Sri Pratap Higher Secondary School}\hfill Jammu and Kashmir, IN\\
Senior Secondary \hfill Nov 2017 - Dec 2019\\
{\sl Percentage: 78.2}\%\\
\vspace{2mm}
      \textbf{JK Public School}\hfill Jammu and Kashmir, IN\\
Secondary \hfill Completed - Oct 2017\\
{\sl Percentage: 82.6}\%\\
\vspace{2mm}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \header{Skills}
  \vspace{2mm}
  \begin{longtable}{p{4cm}p{12cm}}
  Languages: & Python, C, Java, Javascript, HTML, CSS, PHP, Laravel, Shell scripting \\
  Tools / Platforms: & Git, GitHub, AWS Elastic Beanstalk, AWS S3, Linux \\
  Database Technologies: & MySQL, SQLite, MongoDB \\
  \end{longtable}
  \vspace{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Projects
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Projects / Open-Source}
      \vspace{2mm}
      {\textbf{Automata Weaver}}\textbf{ | \href{https://github.com/syedhuzaif199/automata-weaver}{\underline{Link}} | \href{https://syedhuzaif199.github.io/automata-weaver}{\underline{Website}}}\hfill{\sl JavaScript, HTML, CSS}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item  Developed an open source online graphical tool and simulator for Finite automata, Pushdown automata and Turing machines.
\item  Implemented features such as minimization of DFAs, convertion from NFA to DFA, and generation of DFA/NFA from regular expressions.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Physics Simulator}}\textbf{ | \href{https://github.com/syedhuzaif199/physics-simulator}{\underline{Link}}}\hfill{\sl Java}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Developed a 2D physics simulator in Java.
\item Implemented various physics concepts such as gravity, collision detection, and friction.
\item Created a user interface for visualizing the simulation.
\item Added features for adjusting simulation parameters in real-time.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Data Compression Tool}}\textbf{ | \href{https://github.com/syedhuzaif199/data-compression-tool}{\underline{Link}}}\hfill{\sl C}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Built a data compression tool using Huffman coding in C.
\item Implemented algorithms for encoding and decoding data.
\item Designed a command-line interface for user interaction.
\item Achieved significant reduction in file sizes for various types of data.
\end{itemize}
          \vspace*{3mm}
      {\textbf{nn-c}}\textbf{ | \href{https://github.com/syedhuzaif199/nn-c}{\underline{Link}}}\hfill{\sl C}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Developed a small neural networks builder and visualizer using C and raylib.
\item Implemented basic neural network operations such as forward propagation and backpropagation.
\item Created a graphical interface for visualizing the network structure and training process.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Category Tree Renderer}}\textbf{ | \href{https://github.com/syedhuzaif199/category-tree}{\underline{Link}}}\hfill{\sl Python}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Created a tool in Python for generating and rendering random category trees using graphViz.
\item Implemented algorithms for random tree generation.
\item Integrated graphViz for visual representation of the trees.
\item Added options for customizing tree properties such as depth and branching factor.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Conway\textquotesingle{}s Game of Life}}\textbf{ | \href{https://github.com/syedhuzaif199/game-of-life}{\underline{Link}} | \href{https://syedhuzaif199.github.io/game-of-life}{\underline{Website}}}\hfill{\sl JavaScript, HTML, CSS}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Developed a web-based simulator for Conway's Game of Life using JavaScript, HTML, and CSS.
\item Implemented the rules of the game and optimized the simulation for performance.
\item Created an interactive user interface for setting initial conditions and controlling the simulation.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Image filters visualizer}}\textbf{ | \href{https://github.com/syedhuzaif199/image-filters-visualization}{\underline{Link}} | \href{https://syedhuzaif199.github.io/image-filters-visualization}{\underline{Website}}}\hfill{\sl JavaScript, HTML, CSS}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Built a web app for experimenting with image filters using JavaScript, HTML, and CSS.
\item Implemented various image processing algorithms such as blur, sharpen, and edge detection.
\item Created an interactive interface for applying filters.
\item Added support for uploading and processing user images.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Snake Game}}\textbf{ | \href{https://github.com/syedhuzaif199/snake-mongo}{\underline{Link}}}\hfill{\sl Java}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Developed the classic snake game in Java with MongoDB connectivity for high-scores.
\item Implemented game mechanics such as snake movement, food generation, and collision detection.
\item Created a graphical user interface for the game.
\item Integrated MongoDB for storing and retrieving high scores.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Minesweeper in python}}\textbf{ | \href{https://github.com/syedhuzaif199/minesweeper-python}{\underline{Link}}}\hfill{\sl Python}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Created a classic Minesweeper game with a dark theme in Python.
\item Implemented game logic including mine placement, number calculation, and win/loss conditions.
\item Added features for different difficulty levels and a timer.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Play with Spirographs}}\textbf{ | \href{https://github.com/syedhuzaif199/play-with-spirographs}{\underline{Link}}}\hfill{\sl JavaScript, HTML, CSS}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item Developed a simple simulator for animating spirographs using JavaScript, HTML, and CSS.
\item Implemented algorithms for generating spirograph patterns.
\item Created an interactive interface for adjusting parameters such as radius and speed.
\item Added options for saving and exporting generated patterns.
\end{itemize}
          \vspace*{3mm}

    \ 
    \end{document}
